### 2013-09-13 thesis/src/chapters/chapter-3.tex
Added diagrams

\section{Introduction}
In short, platform adaptivity adds a auto-scaling features to a solution offered by Platform-as-a-Service provider. Key concept is to have a Elasticity Controller which gathers probes from virtual machines and uses that knowledge to execute appropriate action on Cloud instance, indirectly modifying consecutive probes \cite{VaRoBu11}. This concept illustrates diagram (IMAGE).

@@

Heroku & ? & ? \\ \hline
\end{tabularx}

>>>>

\section{Introduction}
In short, platform adaptivity adds a auto-scaling features to a solution offered by Platform-as-a-Service provider. Key concept is to have a Elasticity Controller which gathers probes from virtual machines and uses that knowledge to execute appropriate action on cloud instance, indirectly modifying consecutive probes \cite{VaRoBu11}. This concept illustrates diagram \ref{ch3:elasticity-controller}.

\begin{figure}[!ht]
  \begin{center}
    \includegraphics{chapter-3/elasticity-controller}
  \end{center}
  \caption{Elasticity controller}
  \label{ch3:elasticity-controller}
\end{figure}

@@

Heroku & $\times$ & $\times$ \\ \hline
\end{tabularx}
